Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-11-01 manuscript/manuscript.Rmd
remove some pdp description
remove mention of stepwise

For linear models and their generalizations, and some ML models, measures of
variable importance can be obtained from the fitted model structure. In the
case of GLMs, one might observe the magnitudes of the $t$-statistics, step-wise
reduction in information criteria, or out-of-sample performance, whereas
for random forests, one might use out-of-bag errors [@breimanRandomForests2001].
For more complex models, such as the neural network in our case study, we need
to devise another approach.

@@

Note that this proposed plot can be calculated over the dataset or over a
hypothetical dataset in which the value of $x_i^{j}$ is set equal to $z$ for
each record.

>>>>

For linear models and their generalizations, and some ML models, measures of
variable importance can be obtained from the fitted model structure. In the
case of GLMs, one might observe the magnitudes of the estimated coefficients or 
$t$-statistics, whereas
for random forests, one might use out-of-bag errors [@breimanRandomForests2001].
For more complex models, such as the neural network in our case study, we need
to devise another approach.

@@
